### 2020-04-14 paper/spor.tex

\NewScheme{\SPOR}{SPOR}

@@

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel\footnote{%
  There can be many reasons for this and many ways to solve it.
  \Eg \(m\) might be unavailable at the time.
  Signal creates \ac{DH} exponents in advance (before \(m\) is known) and 
  publishes on the Signal servers, so Alice would fetch one of Bob's when she 
  has a message to send.
  We will treat this in more detail later.
}.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as parameter. \sonja{what about the crossover node and
  Alice's leg of the route?} 
Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Bob who identifies the message as the 
one expected to come from Alice.
%(This process is illustrated in \cref{fig:file-transfer}.)
Now we will focus on how Alice and Bob choose the nodes that they provide to 
\(\CreateReply\) and \(\CreateFwd\).

@@

@@

>>>>

@@

Say that Alice wants to send a message \(m\) to Bob.
Bob creates a reply header using \(\CreateReply\) and gives the output to Alice 
over an out-of-band channel\footnote{%
  There can be many reasons for this and many ways to solve it.
  \Eg \(m\) might be unavailable at the time.
  Signal creates \ac{DH} exponents in advance (before \(m\) is known) and 
  publishes on the Signal servers, so Alice would fetch one of Bob's when she 
  has a message to send.
  We will treat this in more detail later.
}.
At a later point, Alice attaches a message \(m\) to the reply header using 
\(\UseReply\), creates a forward header using \(\CreateFwd\) with the prepared 
reply header as parameter.
Then she sends this packet to the first node, which processes it using 
\(\ProcessHeader\).
The node will then process the header and in turn forward the packet to the 
next node.
At some point the message will reach Bob who identifies the message as the 
one expected to come from Alice.
%(This process is illustrated in \cref{fig:file-transfer}.)
Now we will focus on two problems that Alice and Bob have:
first, how Alice and Bob choose the nodes that they provide to \(\CreateReply\) 
and \(\CreateFwd\);
second, how Alice and Bob can reduce the use of the out-of-band channel.

@@

\subsection{Selecting nodes}

@@

\subsection{Reducing the use of the out-of-band channel}

It is desirable for Alice and Bob to use out-of-band communication as little as 
possible.
To do this, we define \ac{SPOR} to let the first part of the payload to be a 
reply header that the recipient can use to reply.
